Presentation Materials

### 2017-03-18 San Antonio/presentation_materials.Rmd
Presentation stuff

---
title: "Presentation Materials"
author: "Yu"
date: "3/13/2017"
output: 
  html_document:
    toc: true
    theme: united
---

@@

@@

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608436 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608791 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4201715 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1518185 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1202215 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 503528 & year < 2013) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1502132 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1510212 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1517165 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1519344 & year < 2011) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "count")
```

>>>>

---
title: "Presentation Materials"
author: "Yu"
date: "3/17/2017"
output: 
  html_document:
    toc: true
    theme: united
---

@@

## Accident Trends

### Fatality since 1983

```{r fatality trend}
# if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
# yearly.death <- complete.active.quarters %>% 
#   filter(year >= 2000 & active) %>%
#   group_by(year) %>%
#   summarise(count = sum(num.death),
#             avg = mean(num.death))
# qplot(x = year, y = count, data = yearly.death, geom = c("point", "line"),
#       main = "Number of Total Fatalities Due to Accidents",
#       xlab = "Year", ylab = "Count")
# # qplot(x = year, y = avg, data = yearly.death, geom = c("point", "line"),
# #       main = "Number of Avgerage Fatalities Due to Accidents",
# #       xlab = "Year", ylab = "Count")
if(!exists("accidents")) {load("./San Antonio/data/secret_ingredients.RData")}
yearly.death <- accidents %>% 
  mutate(death = ifelse(inj_degr_desc == "FATALITY", 1, 0)) %>%
  group_by(cal_yr) %>%
  summarise(count = sum(death))
qplot(x = cal_yr, y = count, data = yearly.death, geom = c("point", "line"),
      main = "Number of Total Fatalities Due to Accidents",
      xlab = "Year", ylab = "Count")
```

### Number of Days Lost since 2000

```{r num.days.lost trend}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.lost <- complete.active.quarters %>% 
  filter(year >= 2000 & active) %>%
  group_by(year) %>%
  summarise(count = sum(num.days.lost),
            avg = mean(num.days.lost))
qplot(x = year, y = count, data = yearly.lost, geom = c("point", "line"),
      main = "Number of Total Days Lost Due to Accidents",
      xlab = "Year", ylab = "Count")
# qplot(x = year, y = avg, data = yearly.lost, geom = c("point", "line"),
#       main = "Number of Average Days Lost Due to Accidents",
#       xlab = "Year", ylab = "Count")
```

### Number of Violations since 2000

```{r viol.quantity trend}
if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(year >= 2000 & active) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity),
            avg = mean(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Total Violations",
      xlab = "Year", ylab = "Count")
# qplot(x = year, y = avg, data = yearly.lost, geom = c("point", "line"),
#       main = "Number of Average Days Lost Due to Accidents",
#       xlab = "Year", ylab = "Count")
```

@@

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608436 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4608791 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 4201715 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1518185 & year < 2006) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1202215 & year < 2007) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 503528 & year < 2013) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1502132 & year < 2010) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1510212 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1517165 & year < 2005) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```

@@

if(!exists("complete.active.quarters")){load("./San Antonio/output/result.RData")}
yearly.viol <- complete.active.quarters %>% 
  filter(mine_id == 1519344 & year < 2011) %>%
  group_by(year) %>%
  summarise(count = sum(viol.quantity))
qplot(x = year, y = count, data = yearly.viol, geom = c("point", "line"),
      main = "Number of Yearly Violations",
      xlab = "Year", ylab = "Count")
```
